Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-02 ms.tex
Update figure captions

\begin{figure*}
\centering
\subfloat[][Two-dimensional slices \label{fig:multidim-incoherent-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_cost_analysis_SKA1-low.pdf}
{figures/multidim_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Two-dimensional slices (relative)\label{fig:multidim-incoherent-relative-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_epic_relative_cost_analysis_LAMBDA-I.pdf}
} 
\caption{(Left): Two-dimensional slices of the computational cost per station per voxel for coherent-incoherent imaging using station-level EPIC. Because the spatial FFT dominates the overall cost budget, the computational cost density is relatively insensitive to $N_\textrm{a/s}$, $D_\textrm{s}$, and $D_\textrm{a}$. (Right): Ratio of computational cost of EPIC to voltage beamforming. For $N_\textrm{a/s}\gtrsim 100$, EPIC has a significant advantage over voltage beamforming Cyan contours indicate nominal values for a \texttt{LAMBDA-I} station. \label{fig:incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[][Two-dimensional slices \label{fig:multidim-incoherent-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Two-dimensional slices (relative)\label{fig:multidim-incoherent-relative-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_dft_relative_cost_analysis_LAMBDA-I.pdf}
}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using a DFT of station-level cross-correlations for \texttt{LAMBDA-I}, \texttt{SKA-low-core}, and \texttt{SKA-low} station parameters (dashed gray lines). Cyan lines denote contours of the colour scale in logarithmic increments. (Right): Same as the left but relative to a voltage beamformer architecture. The computational cost density is dominated by the two-dimensional DFT cost for $t_\textrm{acc}=1$~ms, and is lower than that of voltage beamforming for $N_\textrm{a/s}\lesssim 100$ while getting more expensive with increasing $N_\textrm{a/s}$. \label{fig:incoherent-compcost-XBF-LAMBDA-I}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\subfloat[][Covariant cost density of EPIC architecture \label{fig:multidim-incoherent-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_cost_analysis_SKA1-low.pdf}
{figures/multidim_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Covariant cost of EPIC architecture relative to VBF architecture \label{fig:multidim-incoherent-relative-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_epic_relative_cost_analysis_LAMBDA-I.pdf}
} 
\caption{(Left): Two-dimensional slices of the computational cost per station per voxel for coherent-incoherent imaging using station-level EPIC. Because the spatial FFT dominates the overall cost budget, the computational cost density is relatively insensitive to $N_\textrm{a/s}$, $D_\textrm{s}$, and $D_\textrm{a}$. (Right): Ratio of computational cost of EPIC to voltage beamforming. For $N_\textrm{a/s}\gtrsim 100$, EPIC has a significant advantage over voltage beamforming Cyan contours indicate nominal values for a \texttt{LAMBDA-I} station. \label{fig:incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[][Covariant cost density of XBF architecture \label{fig:multidim-incoherent-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Covariant cost of XBF architecture relative to VBF architecture \label{fig:multidim-incoherent-relative-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_dft_relative_cost_analysis_LAMBDA-I.pdf}
}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using a DFT of station-level cross-correlations for \texttt{LAMBDA-I}, \texttt{SKA-low-core}, and \texttt{SKA-low} station parameters (dashed gray lines). Cyan lines denote contours of the colour scale in logarithmic increments. (Right): Same as the left but relative to a voltage beamformer architecture. The computational cost density is dominated by the two-dimensional DFT cost for $t_\textrm{acc}=1$~ms, and is lower than that of voltage beamforming for $N_\textrm{a/s}\lesssim 100$ while getting more expensive with increasing $N_\textrm{a/s}$. \label{fig:incoherent-compcost-XBF-LAMBDA-I}}
\end{figure*}
